\begin{thebibliography}{1}
%%
%\bibitem{improving_testability}
%G. Yee. (2000). \emph{Improving Software Usability} [Online]. Available: \url{http://www.sce.carleton.ca/faculty/yee/Improving_Testability.pdf}
%%
%\bibitem{abstract_patterns}
%W. Souza, . \emph{Abstract Testability Patterns} [Online]. Available: \url{http://patterns-wg.fuka.info.waseda.ac.jp/SPAQU/proceedings2009/3-P2-AbstractTestabilityPatterns.pdf}
%%
%\bibitem{automation_misconception}
%E. Dustin, T. Garrett, and B. Gauf, \emph{Implementing Automated Software Testing: How to Save Time and Lower Costs While Raising Quality}. Boston, MA: Addison-Wesley Professional, 2009.
%%
%\bibitem{microsoft_asp}
%D. Esposito \emph{Programming Microsoft\textregistered \phantom{ }ASP.NET MVC}. Redmond, WA: Microsoft Press, 2011.
%%
%\bibitem{oo_testability_binder}
%R. Binder, “Design for testability in object-oriented systems,” \emph{Communications of the ACM}, vol. 37, issue 9, September 1994.
%%
%\bibitem{freedman}
%Roy S. Freedman, “Testability of Software Components”,  \emph{IEEE 
%Transactions on Software Engineering}, Vol. 17, No. 6, 1991.
%%
\bibitem{evolve_your_hierarchy}
M. West. (2007). \emph{Evolve Your Hierarchy} [Online]. Available: \url{http://cowboyprogramming.com/2007/01/05/evolve-your-heirachy/}
\bibitem{game_object_structure}
K. Wilson. (2002). \emph{Game Object Structure: Inheritance vs. Aggregation} [Online]. Available: \url{http://gamearchitect.net/Articles/GameObjects1.html}
\bibitem{data_driven_game_objects}
S. Bilas. (2002). \emph{A Data-Driven Game Object System} [Online]. Available: \url{http://scottbilas.com/files/2002/gdc_san_jose/game_objects_slides.pdf}
\bibitem{functional_programming}
J. Carmack. (2012). \emph{Functional Programming in C++} [Online]. Available: \url{http://www.altdevblogaday.com/2012/04/26/functional-programming-in-c/}
\bibitem{functional_programming}
J. Carmack. (2012). \emph{Functional Programming in C++} [Online]. Available: \url{http://www.altdevblogaday.com/2012/04/26/functional-programming-in-c/}
\bibitem{flexible_framework_for_game_development}
M. Haller, W. Hartmann, and J. Zauner. (2022). \emph{A generic framework for game development}. \emph{Proceedings of the ACM SIGGRAPH and Eurographics Campfire}
\bibitem{game_engines}
J. Ward. (2008). \emph{What is a Game Engine?} [Online]. Available: \url{http://www.gamecareerguide.com/features/529/what_is_a_game_.php}
\bibitem{unreal_engine_3}
Game Development Tools for Unreal Engine 3, Unreal Engine. [Online]. Available: \url{http://www.unrealengine.com/en/features/}
\bibitem{cryengine_3}
MyCryENGINE, Crytek. [Online]. Available: \url{http://www.mycryengine.com/}
\bibitem{unity3d}
Game Engine, tools, and multiplatform, Unity. [Online]. Available: \url{http://unity3d.com/unity/}
\bibitem{cocos2d}
Cocos2D for iPhone, Cocos2D. [Online]. Available: \url{http://www.cocos2d-iphone.org/about}
\end{thebibliography}
